Molecular Gas Kinematics and Spectral Energy Distribution Properties of the Strongly-Lensed Quasar Host Galaxy RXS J1131$-$1231

### 2016-12-08 WRITEUP/response.md

We thank the referee for providing constructive and thoughtful
comments that helped us to improve this manuscript. We have addressed all the concerns raised by the referee in the revised version of the manuscript. Our response can be found after each of the referee's points below and are marked by a "#" symbol at the beginning.

@@

"Interpretation of CO, Radio, Optical, and IR Continuum 
observations of the Strongly Lensed Host Galaxy of the 
Quasar RXS J1131-1231"

or simply:

"CO, Radio, Optical, and IR results on 
the Lensed Host Galaxy of the Quasar RXS J1131-1231".

# RESPONSE:
1a) To take the referee's point into account, we have changed the title to "Molecular gas kinematics and spectral energy distribution properties of the strongly lensed quasar host galaxy RXSJ1131-1231". We agree that we study more than just the CO gas of the science target in this paper; however, a large fraction of the paper is based on our new CO data and the analysis (including lens modeling) on which we thus place an emphasis.

@@

Fig.3, caption:
"...z = 0.6537, which corresponds to the dynamical center of CO(2-1)."

Change to :

"..which corresponds to zero velocity in the CO(2-1) spectrum (Fig.1)."

# RESPONSE:
We have taken into account the referee's comment and have updated the CO redshift based on the results from fitting a double-Gaussian to the de-lensed intrinsic line profile of our target (Fig. 5), and we have revised all relevant figures and derived quantities. We have also changed our wording in the caption of Fig. 1 from "dynamical center" to "line center".

@@

The V-band source is smaller (more compact) than the cooler regions in I and H bands,
in the larger spiral disk farther from the nucleus.

So, they interpret the different magnifications as due to different sizes in the source plane.

This is not the same as magnification varying across the line profile,
due to different source-plane positions, as you are claiming.

# RESPONSE:
We agree with the referee's comment and have changed "dynamical information" to "kinematic information", and "reconstruct the intrinsic gas dynamics" to "reconstruct the intrinsic line profile and source-plane velocity structure".

To address the referee's comment, we have re-written the 2nd paragraph of Section 4.1.2. Rather than saying the differential lensing effect in CO is *similar* to what is seen in the optical, we point out that different magnification factors have been reported in previous studies using optical images. This is done to illustrate the prominence of differential lensing effect in this source, and to demonstrate that the CO gas traces a different region in the source plane and has a different spatial distribution compared to the stellar populations.

@@

--- Or else just explain that the V_0 in your Eq(1) comes out to +28 km/s (relative to z=0.6537)
because of the very coarse sampling of your seven 108 km/s-wide bins.

The true line center (relative to z=0.6537) would be at V_0 = +75 km/s if you had
used the full-resolution spectrum (Fig. 1 or Fig.5), rather than the heavily binned channels.

# RESPONSE:
We have corrected nu_LO --> nu_obs.

We agree with the referee and have re-fitted a doubled Gaussian to the de-lensed profile (Fig. 5) to updated the redshift to z=0.6541. We have therefore replotted all the relevant figures (and updated their captions correspondingly), updated column 1 in Table 3 and the labeling in Fig 7, refitted the arctangent model (Fig. 9) and updated parameters in Section 4.3 correspondingly, and refitted SED with the updated redshift.

@@

Does Fig.5 now show the spatially integrated spectrum ? 
What is the difference between this spectrum and the one in Fig.1?

If it is again a spectrum taken at the maximum-intensity point,
then the units on the vertical axis would again have to be [ mJy/beam ].

In Fig.5,it would be good to show what you think is the contribution from the companion galaxy.

# RESPONSE:
The referee is correct and we found a bug in the GILDAS package that affected the statistics and fluxes within the map used for previous line-integrated flux extraction. In the resubmitted version, we have updated the intensity reported for CO(2-1) by summing the fluxes over the FWZI (20.3+/-0.6 Jy km/s). The updated intensity is in agreement with the double-Gaussian fitted to the  extracted spectrum (Fig. 1). Since the lensing-corrected M_gas for both RXJ1131 and the companion are derived by first summing up the flux density of each channel within the FWZI, and then dividing by their respective magnification factors. This revision in the CO line intensity does not change our conclusion of this paper.

We have adopted the suggestion provided by the referee and have updated Fig. 5 to include an additional figure showing the de-lensed spectra for RXJ1131 and the companion.

@@

So the de-magnified RADIUS of the CO source is only 3.5 kpc.

It looks like the intrinsic R_CO = 6 kpc (diameter = 12 kpc)
that you quote elsewhere in the paper is too high:
---Abstract, 
---Sect.4.3, para.3, 
---Sect.4.4, para.1, 
---Sect.5.1.1, para.2,
---Sect.5.5, para.2
---Sect.5.1.1, para.2,
---Sect.6, para.2

# RESPONSE:
Source size: 
We addressed the referee's comment on the *deconvolved* CO source size by fitting a single Gaussian in uv-plane, which corresponds to 4.5" +/- 0.1" x 3.5" +/- 0.2", consistent with the reported CO size based on image-plane fitting within the uncertainties. We additionally report the source sizes by fitting two Gaussians to provide further evidence that the CO(2-1) emission is spatially resolved. We have updated Section 3.1 to clarify the discussion.

CO physical size:
The rough estimate of the de-magnified CO diameter provided in the referee report is a valid first order estimate, but the true size of the source is complicated by the fact that
1) the lensed emission is not uniformly stretched along the arc (and contains complex structures within the arc), and thus the magnification factor is not uniform across the partial Einstein ring. 
2) CO is not subject to dust extinction, and its emission may be more extended than optical emission. In the case of RXJ1131, the CO gas is likely to be more extended than the optical emission given that
    i) the deconvolved source size of CO (see above and section 3.1) is larger than the diameter of the Einstein Ring in the optical (~3.6")
    ii) the spatial extent of the CO emission as shown in Fig. 7, where centroid of the redshifted component is co-spatial with the lensed arc but centroid of the blueshifted component is offset to the SE of the lensed arc, tracing regions beyond the optical emission. 
3) the source-plane distance of ~6.2 kpc between the centroid position of the most extended kinematic component and the line center position. This is also the value we use for reporting R_CO throughout this paper.

See also Section 4.3 and our response to point 14 in this referee report for a more detailed explanation regarding the CO size.

@@

Similarly, in the same paragraph, for the (3-2) / (2-1) ratio,
you could just say 0.7 +/- 0.4 .

In Sect.3.2, para.1, you say the observing frequency is 209 GHz.
So the wavelength is 1.4mm, not 1.5mm. 
(There are two places to fix this).

#RESPONSE
We have considered the referee's point of view, and agree that the most extreme peak to peak noise across two channels is from -50 to +50 mJy/beam. However, this is not representative of the noise across all channels that are being used to derive the line flux. We thus derive the uncertainty based on the RMS obtained from the intensity map.

To address the referee's comment and to demonstrate the significance of our detection that is reported in the paper, we have extracted the peak fluxes and their corresponding uncertainties for the blue and red wing independently. For the blue wing, we find a peak flux density of 5.13 +/- 1.43 Jy km/s /beam in the intensity map, indicating a ≥3sigma detection in this component alone. For the red wing, we find a peak flux density of 11.45+/-1.99 Jy km/s /beam in the intensity map, indicating a ~6 sigma detection. The SNRs are thus consistent with the reported detection significance of ≥5sigma in the paper which was obtained based on the peak flux density in the intensity map obtained by summing over the full line profile (i.e., including emission in both wings).

@@

Instead of calling this the "deblending procedure",
which people might confuse with deconvolution, 
I would just call it "subtraction of the foreground galaxy", 
or "flux removal by subtraction", because it is just simple 
subtraction, not anything else.

# RESPONSE
In the residual map, the peak emission is 0.39 +/- 0.08 mJy. This flux (0.39 mJy) is what we adopted for RXJ1131 at 2mm in the paper. To address the referee's comment, we have updated the uncertainty associated with this measurement by adding those associated with the fitted point-source model and that in the residual map (from which we extracted the flux for RXJ1131) in quadrature (i.e. S_2mm = 0.39+/-0.12 mJy).

The emission in the residual is detected at S/N > 4, which is the significance of the emission in the residual map (Data - Model). This together with the fact that this emission is co-spatial with the lensed arc in the optical image indicates that we detect 2mm continuum towards the background source.

To take into account the referee's comment, we have updated the 2mm flux in Table 1, and the flux uncertainty to include those from the uv-fitting process.

@@

If the 2mm continuum flux is synchrotron emission, like the 6cm VLA continuum flux,
then it is probably unrelated to the stellar mass of the quasar host galaxy.

So I don't understand why you use it in sect.4.5, para.4 to fit 
the Bruzual & Charlot stellar templates.

Any comment on the very flat spectrum for the lensing elliptical galaxy ?
Is the 6cm emission mainly synchrotron? 
Is the 2mm emission a mix of synchrotron flux and dust flux ?

# RESPONSE:
While the radio-mm spectral slope of -0.35+/-0.21 derived for the background source has a large error bar associated with it due to the large uncertainty on the 2mm flux (0.39+/-0.12 mJy), the fact that it is significantly flatter than the typical slope for pure synchrotron emission indicates that it provides a limit on the amount of synchrotron emission at 2mm. Thus, we used this radio-mm spectral slope to estimate the expected flux from synchrotron emission at 2mm, and attribute the residual flux to thermal dust emission.Assuming a synchrotron index of alpha = -0.7 and using the 5GHz flux, we expect S_2mmm = 0.122+/-0.004 mJy to be arising from synchrotron emission. We thus find a flux excess of S_2mm = 0.39 - 0.12 = 0.27 mJy that is coming from thermal dust emission. We have updated our dust SED fitting using S_2mm = 0.27+/-0.08 mJy and the resulting parameters throughout the paper.

We note that 0.27+/-0.08 mJy is consistent with our previous flux measurement used for SED fitting (0.39+/-0.12 mJy, including uncertainties from absolute flux calibration) within the uncertainties. Therefore changes to the physical parameters derived from SED fitting are only at most a few percent. We have updated the relevant quantities but this does not alter the conclusions of this paper.

Flat spectrum of foreground galaxy:
We have also added a statement in the paper stating that if the background source has a contribution in the point-source model assumed in our deblending procedure, such that its flux density would be higher than derived here (0.39 +/- 0.12 mJy), then the derived spectral index (-0.35) would be even shallower.
In this case, the 2mm flux inferred for the foreground galaxy would lower, and thus steepening its spectral slope. Hence, a contribution from the background source to the point-source model 2mm flux may explain the atypical flat spectrum found for the foreground galaxy. Alternatively, the foreground galaxy could be a core-dominated radio objects, and thus displays a flat spectrum.

@@

--- the CO(3-2) similar parameters (when possible).

--- the L'co luminosities corrected for lensing (RXJ1131 + companion).

--- the M(H2) estimated from the CO luminosity (main source + companion).

The same is true of the derived quantities. 
Possible add another Table summarizing the other derived quantities:

@@

--- the black hole mass

--- the M_BH / M_bulge ratio.

Otherwise, the reader has to search for all these CO values and other quantities in 
many different parts of the text.

# RESPONSE:
We adopted these good suggestions and have added additional tables (Table 1 and 6) summarizing the observed CO line properties and the derived physical parameters.

@@

So S(6cm) = 0.87 +/- 0.09 .

So you need not quote these fluxes to three decimal places.

Because of these flux errors, you also cannot quote the spectral
index of the foreground galaxy to three decimal places
(Sect. 3.3, last sentence).

# RESPONSE:
It is the standard practice to report flux measurement uncertainties from interferometric observations separate from those due to absolute flux calibration and state those in the observations section (i.e. Section 2). However, we note that uncertainties from absolute flux calibration are taken into account when deriving the error bars associated with physical parameters throughout the paper. To address the referee's concern, we have added remarks in Table 1, and Section 4.5 paragraph 1 to remind the reader of these uncertainties.

We have updated the number of decimals in the spectral indices indexes reported in Section 3.3, as suggested by the referee.

@@

Because the lensing galaxy is so strong on the VLA map (Fig.4), one
cannot count the contours on the central source. 
So in the caption, 
it might be good to say how many contours there are up to the peak
(= 22 contours ?), and that this corresponds to a flux of 0.9 mJy/b.

An alternative would be to change the contour step after 3 contours
in the VLA map, so that the higher contours would become visible.

But it is probably easiest to just explain the peak value in 
the figure caption.

# RESPONSE
We agree with the referee and have revised Fig. 4 by using a different contour interval for the VLA data and changed the linewidths of the contours. We have also updated the caption to illustrate the significance of the radio detection towards RXJ1131.

@@

Also wrong, here.

Should be "... our CO observations confirm the redshifted BLR lines."

not "blueshifted".

# RESPONSE:
We have corrected "blueshifted" to "redshifted", updated the velocity offset from 780 km/s to 715 km/s using z = 0.6541, as suggested by the referee.

@@

Because the NLR is big (100 pc), it is not affected by microlensing.
Because the BLR is small, it is affected by
microlensing in this quasar (Sluse et al.).

It could also be that the microlensing more strongly magnifies
the redshifted part of the BLR lines, 
biasing the apparent redshift to the red side.

2) BLUE SIDE OF THE LINE ATTENUATED BY ABSORPTION :

Another possibility is that the BLR shows mainly rotation 
in the accretion disk, and also a biconical outflow region
from the outer parts of the accretion disk, as in the BAL phenomenon.

@@

So in one rotation time of the host galaxy, 
or in one orbital time of the companion galaxy, 
or in the duration of the starburst, 
or in the duration of the "wet merger" 
(all of these are ~1E8 years), 
the black hole would have moved quite far away from the center of the host galaxy
(10 to 100 kpc !).

This also makes the recoil story implausible, especially for 
many other catalogued quasars and Seyfert galaxies that have differences
between the peaks of the NLR lines and the BLR lines.

# RESPONSE:
We have removed the statement regarding "AGN dynamically offset", as suggested by the referee.

1) & 2)
Our CO measurement provides the most precise value for the velocity offset between the BLR and the host galaxy. We thus feel that this is an invaluable addition to the literature.

We acknowledge that velocity offsets between BLR and NLR lines are quite common in Seyferts and quasars, but the offsets as large as that of RXJ1131 appear to be uncommon according to the distribution of offset among other AGN hosts (Richards+02, Bonning+07). To take into account the referee's comments, we have updated this section by including a brief discussion on other possible interpretations for the velocity offset (e.g. gas inflows, geometric effects), as outlined in detail by the referee.

@@

Both of these sections are very well-written, but will probably be
completely incomprehensible to many readers (including me).

I suggest that you just say that you did best fits to model the lens distribution
and best fits to the SED. 
Simply give a typical reference to the Markov chain, Monte Carlo method.

# RESPONSE:
The details of the model (e.g. how we reconstruct the likelihood functions) are described in other papers, which we reference to in the paper for brevity.

However, the description of our MCMC sampling has been retained since stating the priors and the methods to ensure convergence are necessary to make results reproducible, and provide crucial information for readers to decide how trust-worthy our inference are from a statistical viewpoint. Explicitly stating the priors is important to demonstrate that our choice are reasonable and physically motivated since they could affect the marginal posteriors strongly, and thus the inferred physical parameters. We therefore decided to keep them in the lens modeling (Section 4.1) and SED fitting sections (Section 4.5).

@@

OMIT THE REST OF THIS PARAGRAPH,

starting with "This implies that the AGN is offset from the dynamical
center of its host galaxy." all the way to the end to the paragraph.

This is not true. The AGN could be at the center of the galaxy,
and the Doppler shift could just be a radial component (inflow),
superposed on the very fast rotational velocity of the accretion disk.

# RESPONSE:
We have updated f_gas and f_mol considering RXJ1131 and the companion as one system. That is, we have used the total M_gas obtained by summing up M_gas of RXJ1131 and of the companion in deriving f_gas, and the total M_dyn obtained by summing up M_gas of RXJ1131 and of the companion in deriving f_mol.

@@

Could another interpretation be that instead of tracing a monotonic p-v diagram,
there are, within the errors, just two little clusters of points in the left panel?
---The upper (red wing) cluster and the lower (blue wing) cluster?
Within the errors, the 3 crosses in the red clump almost agree in position,
and the 4 crosses in the blue clump almost agree in position, as well.

The separation between the centroids of the two clusters of points is 1 arcsec, or 7 kpc.
So if this is a central disk, then within the errors, its radius is only 3.5 kpc, not 
the 6 kpc that you quote in many places in the text.

Why do these two clusters of points in Fig.9 (left) not appear in your
p-v diagram in Fig.9 (right)?
In the right panel, why do all the little crosses seem to be evenly spaced?
Is the right panel based on an additional model of a rotating disk, rather than 
the lens model points in Fig.9 (left)?

# RESPONSE:
Indeed, the plot on the left is to demonstrate that while the observed 1st moment map is distorted due to a combination of differential lensing and beam smearing effects, our dynamical lens modeling approach, which finds the best-fit models by taking into account the beam convolution indirectly, has enabled us to reconstruct the source-plane positions for different kinematic components. Therefore, we show the source-plane positions atop of the observed 1st moment map. To address the referee's concern, we have added some additional description to the caption to clarify what is being shown in the left panel.

The reconstructed source-plane positions display a clear velocity gradient that is reminiscent of a rotating disk-like object. Taken together with previous results from literature (C06) and the intrinsically symmetric line profile (Fig. 5), we carried out dynamical modeling in Section 4.3 assuming RXJ1131 is a disk galaxy.

PV: 
We have detailed the reasons for why we interpret RXJ1131 as a disk galaxy in Section 4.1.1. Under this assumption, the markers on the right plot are based on extracting along a fitted major axis of a disk (see first paragraph of Section 4.3).

To address the referee's concern and to improve the clarity of this section, we have added the following at the beginning of Section 4.3 to remind the reader that we are assuming RXJ1131 to be a disk galaxy for dynamical modeling.

"As discussed in §4.1.1, we interpret RXJ1131 as a disk galaxy as it displays evidence of a source-plane velocity gradient in the CO emission, a symmetric double-horned line profile (Figure 5, Figure 6 and, left panel of Figure 9), and a disk-like morphology in the source-plane reconstruction of optical-NIR emission (C06)"

Size:
As explained in paragraph 3 of Section 4.3, we use the maximum observed velocity (i.e.  corresponding to the red-most channel along the disk major axis) at 6+/-3 kpc as a proxy for the rotation velocity. Thus the quoted CO disk radius corresponds to the extent of this velocity component, as measured from the centroid position at zero velocity.

### 2016-12-08 WRITEUP/ms.tex
ready for DR again

\input{preamble}
\slugcomment{To be submitted to the ApJ}
 \makeatletter
% \renewcommand\normalsize{\@setfontsize\normalsize\@xpt{11.56}}
\renewcommand\normalsize{\@setfontsize\normalsize{10.56}{11.4}}
\makeatother

@@

\begin{document}
%{\tiny  \RevisionInfo}

\title{Molecular Gas Kinematics of the Strongly-Lensed Quasar Host Galaxy RXS J1131$-$1231}
\author{T. K. Daisy Leung, Dominik A. Riechers, and Riccardo Pavesi}
\affil{Department of Astronomy, Space Sciences Building, Cornell University,
Ithaca, NY 14853, USA; \myemail}

@@

\subsection{CARMA \cco}
Observations of the \cco rotational line 
($\nu_{\rm rest}$\,=\,345.79599\,GHz) redshifted to $\nu_{\rm obs}$\eq209.10443\,GHz
towards RXJ1131 at $z_{\rm QSO}$\eq0.658 
were carried out with the \carma (CARMA;
Program ID: cf0098; PI: D. Riechers) in the D array configuration. They were carried out
on 2014 February 02 under poor 1.5\,mm
weather conditions and on 2014 February 17 under good 1.5\,mm
weather conditions.
This resulted in a 
total on-source time of 2.94 hours after flagging poor
visibility data.
The correlator setup provides a bandwidth of 3.75 GHz in
each sideband and a %native
spectral resolution of 12.5 MHz ($\sim$17.9 \kms). The
line was placed in the lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$216 GHz. The radio quasars J1127$-$189 (first track) and 3C273
(second track) were observed
every 15 minutes for pointing, amplitude, and phase calibration. Mars was
observed as the primary absolute flux calibrator and 3C279 was observed as
the bandpass calibrator for both tracks.

@@

The \ncode{miriad} package was used to calibrate the visibility data.
The calibrated visibility data were
imaged and deconvolved using the CLEAN algorithm with ``natural'' weighting. This yields a synthesized clean
beam size of 3\farcs2 $\times$ 1\farcs9 (PA\,=\,8\degr) for the lower sideband
image cube. The final rms noise is $\sigma$ = 13.3 mJy beam$^{-1}$
over a channel width of 25\,MHz. An rms noise of
$\sigma$\,=\,0.83\,mJy\,beam\pmOne is reached by averaging over the
line-free channels in both sidebands.

\subsection{PdBI \bco}
Observations of the \bco rotational line
($\nu_{\rm rest}$\,=\,$230.53800$ GHz) 
redshifted to $\nu_{\rm obs}$\eq139.256\,GHz towards RXJ1131
at the
CARMA \cco redshift of $z_{\rm CO(3-2)}$\eq0.655
were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
Riechers).
Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively.
This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
 time after discarding unusable visibility data.
The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup that provides
an effective bandwidth of 3.6 GHz (dual polarization) and a native spectral resolution of 1.95\,MHz
($\sim$\,$4.2$\,\kms).
The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as primary flux calibrators for the C and D
array observations, respectively, yielding calibration accuracy better than 15\%.

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{Continuum-subtracted spectrum (histogram) of \bco emission towards RXJ1131, with a spectral resolution of
22\,\kms. The solid black line shows a double-Gaussian fit to the line profile.
The velocity scale is with respect to $z$\,=\,0.6541, which corresponds to the line center of RXJ1131 based on
the de-lensed line profile (\Fig{delensed}).
A detailed discussion of this effect is presented in \Sec{differential}. \label{fig:CO21spec}}
\end{figure}
\vspace{.2em}
% moment 0 map, highest SNR: CASA chan=125~159 <=> GILDAS 126-160 <=> python 125-160
% - sigma = 0.305 Jy km/s/Beam
%   - note that theoretical sigma is lower = 1.5 * sqrt(160-126+1) * 21.5 ~ 0.2 Jy km/s /beam, due to higher noise in some channels with emission
We construct a zeroth order moment map, red/blue channel maps, and
first and second moment maps, as shown in \Fig{CO21mom},
using the $uv$-continuum subtracted data cube over a velocity range of
$\Delta v$ $\sim$ 750\,\kms.
The higher-order moment maps are produced using
unbinned channel maps with 3$\sigma$ clipping.
The peak flux density is 8.12\pmm0.30 Jy\,\kms\,beam\pmOne
in the intensity map.
Observed properties of the \bco emission line are summarized in \Tab{obsprop}.

The deconvolved source size FWHM from fitting a single two-dimensional Gaussian 
to the integrated line image yields 5\farcs1\pmm0\farcs7$\times$3\farcs7\pmm0\farcs7,  % In the image plane, the *convolved* size is 6.6"+/-0.5" x 4.5"+/-0.3". 
consistent with that obtained by $uv$-plane fitting within the uncertainties. 
% UV plane: E_GAUSS: 4.5 +/- 0.1 x 3.5 +/- 0.2
The spatial distribution of the observed CO emission is unlikely to be fully 
encapsulated by a simple Gaussian 
given its skewed emission, which also appears to be a superposition of two components (\Fig{CO21mom}). 
% To better capture the spatial distribution of the line emission, we 
We therefore also fit a model of two Gaussians which yeilds deconvolved source sizes of 
3\farcs8\pmm0\farcs4$\times$1\farcs9\pmm0\farcs4 and 3\farcs6\pmm0\farcs3$\times$1\farcs5\pmm0\farcs3, respectively.
The deconvolved source size together with
% complex morphology of a partial ``Einstein ring'' with 
% structures along the arc and knots 
% seen in optical and \nir emission (see \Fig{CO21mom}). %that were observed at higher resolution, 
the spatially more extended blue wing compared to the optical 
``Einstein ring" of diameter $\sim$3\farcs6 (top right panel of \Fig{CO21mom}) suggest that 
the CO-emitting region in RXJ1131 is more extended than its stellar and quasar emission.

\begin{figure*}[!htbp]
\hspace{0.5em}
% total chan range = 126-160, which is consistent with mom0 map now (see 15May16)
% 126-144 (Red)
% ~ delta V ~410 km/s
% from [409, 0] km/s
%  144-160 (Blue)
% ~ 365 km/s
% [-324.88, 0] km/s
\includegraphics[trim=0 10 15 0, clip, width=0.452\textwidth]{../Figures/F555WCO21_mom0_single_invertedgray.eps}
\includegraphics[trim=5 -18 0 0, clip, width=0.462\textwidth]{../Figures/F555W_REDBLUE.eps}
\\
\includegraphics[trim=25 16 0 10, clip, width=0.85\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
\vspace{0.1em}
\caption{Top left: overlay of the velocity-integrated \bco emission on an archival {\it HST} $V$-band (F555W)
image.
Top right: same as top left, except the contours are color-coded to represent the red- and blueshifted emission, which
are extracted by integrating over $v$\,$\in$[$-$19, 357] \kms and $\in$[$-$395, $-$19] \kms, respectively.
The contours in both top panels start at 3$\sigma$ and increment at steps of
$\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne for the top left panel,
and
$\sigma$ = 0.4 mJy beam\pmOne (red) and 0.5 mJy beam\pmOne (blue)
for the top right panel.
The crosses denote the
location of the foreground galaxy at $z$\,=\,0.295.
Contours for the first (bottom left) and second (bottom right) moment maps of the \bco line emission
are shown in steps of
50 \kms, and 100 \kms, respectively.
The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$.
\label{fig:CO21mom}}
\end{figure*}

@@

\subsection{Systemic Redshift and Velocity Offset}
%Outflow:
% require different velocity offsets in Balmer and forbidden lines (Zamanov02a)
% line origins:
% \mgii & Hbeta: outer part of the BLR (Goad12a) compared to high-ionization lines (\eg CIV)
% Hbeta can also come from NLR

>>>>

\input{preamble}
\slugcomment{To be submitted to the ApJ, with changes from the referee report }
 \makeatletter
% \renewcommand\normalsize{\@setfontsize\normalsize\@xpt{11.56}}
\renewcommand\normalsize{\@setfontsize\normalsize{10.56}{11.4}}
\makeatother

@@

\begin{document}

\title{Molecular Gas Kinematics and Spectral Energy Distribution Properties of the Strongly-Lensed Quasar Host Galaxy RXS J1131$-$1231}
\author{T. K. Daisy Leung, Dominik A. Riechers, and Riccardo Pavesi}
\affil{Department of Astronomy, Space Sciences Building, Cornell University,
Ithaca, NY 14853, USA; \myemail}

@@

\subsection{CARMA \cco}
Observations of the \cco rotational line 
($\nu_{\rm rest}$\,=\,345.79599\,GHz) towards RXJ1131 at $z_{\rm s, QSO}$\eq0.658 
were carried out with the \carma (CARMA;
Program ID: cf0098; PI: D. Riechers) in the D array configuration. 
The line frequency is redshifted to $\nu_{\rm obs}$\eq209.10443\,GHz at the quasar redshift.
Observations were carried out
on 2014 February 02 under poor 1.5\,mm
weather conditions and on 2014 February 17 under good 1.5\,mm
weather conditions.
This resulted in a 
total on-source time of 2.94 hours after flagging poor
visibility data.
The correlator setup provides a bandwidth of 3.75 GHz in
each sideband and a %native
spectral resolution of 12.5 MHz ($\sim$17.9 \kms). The
line was placed in the lower sideband with the local oscillator tuned to $\nu_{\rm LO}\sim$216 GHz. The radio quasars J1127$-$189 (first track) and 3C273
(second track) were observed
every 15 minutes for pointing, amplitude, and phase calibration. Mars was
observed as the primary absolute flux calibrator and 3C279 was observed as
the bandpass calibrator for both tracks.

@@

The \ncode{miriad} package was used to calibrate the visibility data.
The calibrated visibility data were
imaged and deconvolved using the CLEAN algorithm with ``natural'' weighting. This yields a synthesized clean
beam size of 3\farcs2 $\times$ 1\farcs9 at a position angle (PA) of 8\degr for the lower sideband
image cube. The final rms noise is $\sigma$ = 13.3 mJy beam$^{-1}$
over a channel width of 25\,MHz. An rms noise of
$\sigma$\,=\,0.83\,mJy\,beam\pmOne is reached by averaging over the
line-free channels in both sidebands.

\subsection{PdBI \bco}
Observations of the \bco rotational line
($\nu_{\rm rest}$\,=\,$230.53800$ GHz) 
towards RXJ1131
were carried out using IRAM \pdbi (PdBI; Program ID: S14BX; PI: D.
Riechers).
Based on the CARMA \cco line redshift of $z_{\rm CO(3-2)}$\eq0.655,
the \bco line is redshifted to $\nu_{\rm obs}$\eq139.256\,GHz.
Two observing runs were carried out on 2014 December 06 and 2015
February 05 under good weather conditions in the C and D array configurations,
respectively.
This resulted in 3.75 hours of cumulative six antenna-equivalent on-source
 time after discarding unusable visibility data.
The 2 mm receivers were used to cover the redshifted \bco line
and the underlying continuum emission, employing a correlator setup that provides
an effective bandwidth of 3.6 GHz (dual polarization) and a native spectral resolution of 1.95\,MHz
($\sim$\,$4.2$\,\kms).
The nearby quasars B1127$-$145 and B1124$-$186 were observed every 22 minutes
for pointing, secondary amplitude, and phase calibration, and B1055$+$018 was
observed as the bandpass calibrator for both tracks.
MWC349 and 3C279 were observed as primary flux calibrators for the C and D
array observations, respectively, yielding calibration accuracy better than 15\%.

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{Continuum-subtracted spectrum (histogram) of \bco emission towards RXJ1131, with a spectral resolution of
22\,\kms. The solid black line shows a double-Gaussian fit to the line profile.
The velocity scale is with respect to $z$\,=\,0.6541, which corresponds to the line center of RXJ1131 based on
the de-lensed line profile (\Fig{delensed}).
A detailed discussion of this effect is presented in \Sec{differential}. \label{fig:CO21spec}}
\end{figure}

% moment 0 map, highest SNR: CASA chan=125~159 <=> GILDAS 126-160 <=> python 125-160
% - sigma = 0.305 Jy km/s/Beam
%   - note that theoretical sigma is lower = 1.5 * sqrt(160-126+1) * 21.5 ~ 0.2 Jy km/s /beam, due to higher noise in some channels with emission
We construct a zeroth order moment map, red/blue channel maps, and
first and second moment maps, as shown in \Fig{CO21mom},
using the $uv$-continuum subtracted data cube over a velocity range of
$\Delta v$ $\sim$ 750\,\kms.
The higher-order moment maps are produced using
unbinned channel maps with 3$\sigma$ clipping.
The peak flux density is 8.12\pmm0.30 Jy\,\kms\,beam\pmOne
in the intensity map.
Observed properties of the \bco emission line are summarized in \Tab{obsprop}.

The deconvolved source size FWHM obtained from fitting a single two-dimensional Gaussian 
to the integrated line emission in the image plane yields 5\farcs1\pmm0\farcs7$\times$3\farcs7\pmm0\farcs7,  
% In the image plane, the *convolved* size is 6.6"+/-0.5" x 4.5"+/-0.3". 
which is consistent with that obtained by visibility-plane fitting within the uncertainties. 
% UV plane: E_GAUSS: 4.5 +/- 0.1 x 3.5 +/- 0.2
Since the spatial distribution of the observed CO emission is unlikely to be fully described by a simple Gaussian
and appears to be a superposition of two components (top left panel of \Fig{CO21mom}), 
we also fit two Gaussians to the intensity map. 
This yields deconvolved source sizes of 
3\farcs8\pmm0\farcs4$\times$1\farcs9\pmm0\farcs4 and 3\farcs6\pmm0\farcs3$\times$1\farcs5\pmm0\farcs3, respectively.
The deconvolved source sizes of both models suggest that the gravitationally lensed CO emission is more extended 
than the optical 
``Einstein ring'', which has a diameter of $\sim$3\farcs6
(i.e., the ``Einstein ring'' formed by CO emission is likely to have a larger diameter compared to the optical one). 
This is consistent with the centroid position of the redshifted emission, which is along the quasar arc seen in the optical image, 
and the blueshifted emission, which is offset further to the SE (top right of \Fig{CO21mom}).
Therefore, the CO-emitting region in RXJ1131 is likely to be more extended than its stellar and quasar emission.

\begin{figure*}[!htbp]
\hspace{0.5em}
% total chan range = 126-160, which is consistent with mom0 map now (see 15May16)
% 126-144 (Red)
% ~ delta V ~410 km/s
% from [409, 0] km/s
%  144-160 (Blue)
% ~ 365 km/s
% [-324.88, 0] km/s
\includegraphics[trim=0 10 15 0, clip, width=0.452\textwidth]{../Figures/F555WCO21_mom0_single_invertedgray.eps}
\includegraphics[trim=5 -18 0 0, clip, width=0.462\textwidth]{../Figures/F555W_REDBLUE.eps}
\\
\includegraphics[trim=25 16 0 10, clip, width=0.85\textwidth]{../Figures/CO_highOmom_CLIP5sigma}
\vspace{0.1em}
\caption{Top left: overlay of the velocity-integrated \bco emission on an archival {\it HST} $V$-band (F555W)
image.
Top right: same as top left, except the contours are color-coded to represent the red- and blueshifted emission, which
are extracted by integrating over $v$\,$\in$[$-$19, 357] \kms and $\in$[$-$395, $-$19] \kms, respectively.
The contours in both top panels start at 3$\sigma$ and increment in steps of
$\pm$3$\sigma$, where $\sigma$\,=\,0.3 mJy beam\pmOne for the top left panel,
and
$\sigma$ = 0.4 mJy beam\pmOne (red) and 0.5 mJy beam\pmOne (blue)
for the top right panel.
The crosses denote the
location of the foreground galaxy at $z$\,=\,0.295.
Contours for the first (bottom left) and second (bottom right) moment maps of the \bco line emission
are shown in steps of
50 \kms, and 100 \kms, respectively.
The synthesis beam size is 4\farcs4 $\times$ 2\farcs0, at PA = 13$\degr$.
\label{fig:CO21mom}}
\end{figure*}

@@

\subsection{Systemic Redshift and Velocity Offset}
%Outflow:
% require different velocity offsets in Balmer and forbidden lines (Zamanov02a)
% line origins:
% \mgii & Hbeta: outer part of the BLR (Goad12a) compared to high-ionization lines (\eg CIV)
% \oiii is forbidden, must be from low-density region (further out)
% Hbeta can also come from NLR
